Dataset table

### 2017-12-12 analyses/04-table-datasets.Rmd
Small edits

---
title: "Table compiler"
author: "Thomas Guillerme"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_width: 12
    fig_height: 12
---

# Compiling the tables for the paper

>>>>

---
title: "Dataset table"
author: "Thomas Guillerme"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_width: 12
    fig_height: 12
---

# Compiling the dataset table
